The last 6 months in NXP Semiconductors was truly an amazing experience. The project was challenging and intriguing at the same time. I would like to take this opportunity to thank few people (to keep it short) who helped me during this project period. My supervisors at NXP, Gerardo Daalderop, and Bart Vermeulen helped me stay motivated and right-on-track all the time with their enthusiasm and dynamic decisions. My supervisor at the University, Majid Nabi Najafabadi, with his guidance, periodic instructions and advice helped me fulfill all the academic requirements to complete this project successfully. I would like to express my gratitude to Joost van Doorn who helped me in critical situations. I would also like to thank Lars van Meurs, Han Raajimakers, Oswald Moonen and Stefan Drude who helped me understand challenging topics. 

I also extend my thanks to my friends Josep Stalin Maria Jebamalai, Sai Janani Ramachandran, Anand Bhaskaran Chethan Shettar, Mridul Krishna and Shivaram Singh Rajput who are my constant pillars of support at all times and helped me stay positive and inspired.

I would like to thank my parents and my family for supporting me and encouraging me to pursue my Master's studies in Europe.  

I would also like to thank EIT ICT Labs for providing me with this great opportunity to be a part of two top-notch European Universities (Technical University of Berlin, Germany and Technical University of Eindhoven, Netherlands). Their continuous support and guidance during the past two years were invaluable.